How has the Brazilian Amazon been constructed as a problem? The economy, the environment, the people, and the nation in the presidential speeches since 1985

### 2022-05-13 Draft_April_2022/Full_draft_20220401.rmd
Added notes about multinomial regression possible issues

```{r multimonial model, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
adr <- data.frame(year = c(1985, 1986, 1987), def_year = c(21.050, 21.050, 21.050))
amazon_def_year <- rbind(adr, amazon_def_year)
ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") # merge
ama_model <- dplyr::left_join(ama_model, AAI, by = "year") # merge
ama_model <- filter(ama_model, location_cat != "Non Identified", mx_cat != "Other Mixed-types") %>% 
  mutate(mx_cat = factor(mx_cat, levels = c("Pure Conservation", "Pure Economic Integration",
                                            "Pure Social Development", "Pure Sovereignty", "Economic Conservation",
                                            "Economic and Social Development", "Sovereign Conservation",
                                            "Sustainable Development","Sovereign Integration",
                                            "Social Conservation", "Other")),
         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018", year), 1, 0))
# model
model <- multinom(mx_cat ~ location_cat + election_year + def_year + AAI, data = ama_model, model = TRUE, trace = FALSE)
# summary statistics
model_summary <- summary(model)
p_values <- round((1 - pnorm(abs(summary(model)$coefficients/summary(model)$standard.errors)))*2, 5)

# too much information... Let's just focus on what we want here...
md <- tibble("Dependent Variable" = c("Economic Integration vs Environmental Conservation",
                                           "Social Development vs Environmental Conservation",
                                           "Sovereignty vs Environmental Conservation"),
                 "Brasilia vs Amazonian States" = c("-1.024*** (0.169)","-1.002*** (0.205)", "-0.206 (0.260)"),
                 "International vs Amazonian States" = c("-0.612*** (0.192)", "-1.583*** (0.303)", "-1.427*** (0.431)"),
                 "Other States vs Amazonian States" = c("0.023 (0.197)", "-0.041 (0.230)", "0.324 (0.302)"),
                 "Election Year" = c("-0.241 (0.186)", "0.028 (0.215)", "-0.684** (0.298)"),
                 "Annual Deforestation" = c("0.063*** (0.013)", "-0.031* (0.016)", "0.004 (0.019)"),
                 "Average Inflation" = c("-0.001*** (0.0001)", "-0.001*** (0.0002)", "-0.0001 (0.0002)"))

kbl(t(md), booktabs = T, caption = "Amazon Problem-Construction by Location", align = "c") %>%
  kable_styling(latex_options = c("striped", "scale_down"), position= "center", font_size = 9, full_width = TRUE) %>%
  footnote(general = c("The multinomial regression coefficients are displayed in log odds.", "Standard errors are displayed in parentheses.","*** for p-value ≤ 0.001", "** for p-value ≤ 0.01", "* for p-value ≤ 0.05.")) %>% 
  column_spec(1, width="5 cm", bold=TRUE, latex_valign = "m") %>%
  column_spec(2, width="5cm", latex_valign = "m") %>%
  column_spec(3, width = "5cm", latex_valign = "m") %>%
  column_spec(4, width = "5cm", latex_valign = "m")
```

>>>>

```{r multimonial model, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
adr <- data.frame(year = c(1985, 1986, 1987), def_year = c(21.050, 21.050, 21.050))
amazon_def_year <- rbind(adr, amazon_def_year)
ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") # merge
ama_model <- dplyr::left_join(ama_model, AAI, by = "year") # merge
ama_model <- filter(ama_model, location_cat != "Non Identified", mx_cat != "Other Mixed-types") %>% 
  mutate(mx_cat = factor(mx_cat, levels = c("Pure Conservation", "Pure Economic Integration",
                                            "Pure Social Development", "Pure Sovereignty",
                                            "Economic Conservation",
                                            "Economic and Social Development", "Sovereign Conservation",
                                            "Sustainable Development","Sovereign Integration",
                                            "Social Conservation", "Other")),
         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018", year), 1, 0))
# model
model <- multinom(mx_cat ~ location_cat + election_year + def_year + AAI, data = ama_model, model = TRUE, trace = FALSE)
# summary statistics
model_summary <- summary(model)
p_values <- round((1 - pnorm(abs(summary(model)$coefficients/summary(model)$standard.errors)))*2, 5)
# too much information... Let's just focus on what we want here...
md <- tibble("Dependent Variable" = c("Economic Integration vs Environmental Conservation",
                                           "Social Development vs Environmental Conservation",
                                           "Sovereignty vs Environmental Conservation"),
                 "Brasilia vs Amazonian States" = c("-1.024*** (0.169)","-1.002*** (0.205)", "-0.206 (0.260)"),
                 "International vs Amazonian States" = c("-0.612*** (0.192)", "-1.583*** (0.303)", "-1.427*** (0.431)"),
                 "Other States vs Amazonian States" = c("0.023 (0.197)", "-0.041 (0.230)", "0.324 (0.302)"),
                 "Election Year" = c("-0.241 (0.186)", "0.028 (0.215)", "-0.684** (0.298)"),
                 "Annual Deforestation" = c("0.063*** (0.013)", "-0.031* (0.016)", "0.004 (0.019)"),
                 "Average Inflation" = c("-0.001*** (0.0001)", "-0.001*** (0.0002)", "-0.0001 (0.0002)"))

kbl(t(md), booktabs = T, caption = "Amazon Problem-Construction by Location", align = "c") %>%
  kable_styling(latex_options = c("striped", "scale_down"), position= "center", font_size = 9, full_width = TRUE) %>%
  footnote(general = c("The multinomial regression coefficients are displayed in log odds.", "Standard errors are displayed in parentheses.","*** for p-value ≤ 0.001", "** for p-value ≤ 0.01", "* for p-value ≤ 0.05.")) %>% 
  column_spec(1, width="5 cm", bold=TRUE, latex_valign = "m") %>%
  column_spec(2, width="5cm", latex_valign = "m") %>%
  column_spec(3, width = "5cm", latex_valign = "m") %>%
  column_spec(4, width = "5cm", latex_valign = "m")

# #####
# # Mixed effects multinomial regression with model controls for president
# # Should we consider this method? We might have time effects?
# # See: https://onlinelibrary.wiley.com/doi/abs/10.1002/sim.1522?casa_token=Ui3Ya1qHE7cAAAAA:_a4xLBxFfsU5I2C7eP0hY-__55UurKhRfvpShTCCdiYO8aVmVV9aqJMWYzrLAg2DXAP5czu5h3yu-sUT 
# m1 <- mclogit::mblogit(mx_cat ~ location_cat + election_year + def_year + AAI,
#                        random = ~ 1|president, data = ama_model)
# summary(m1)
# # what about the independence of our response categories? Maybe we should fit a mutinomial probit model
# # the package MNP does this but it is not clear that MNP is better even if IIA (see: file:///Users/henriquesposito/Downloads/Choosing_between_multinomial_logit_and_multinomial_probit_models_for_analysis_of_unordered_choice_data_accessible.pdf)
# m2 <- MNP::mnp(mx_cat ~ location_cat + election_year + def_year + AAI, data = ama_model)
# summary(m2)
# #####
```
